HO unification from object language to meta language

### 2024-04-03 paper/main.tex
some rework

TODO: W preservation \cref{prop:nf}

@@

\newcommand{\progressetaright}{\emph{progress-$\eta$-right}}
\begin{definition}[\progressetaright]\label{def:progressetaright}
A link \linketaM{\Gamma}{X}{T} is removed from \linkStore when
$\testmaybeeta~T$ does not hold (anymore) and by $\eta$-contracting
$T$ to $T'$ (if possible, else $T' = T$) and executing $X \Ue{} T'$ (under
the context $\Gamma$).
\noteE[inline]{there was a note about T' having a rigid head, TO BE FIXED}
\end{definition}

There is a third case in which a link is removed from \linkStore, namely
when the \lhs is assigned to another variable that is the \lhs of another
\linketa.

>>>>

@@

\newcommand{\progressetaright}{\emph{progress-$\eta$-right}}
\begin{definition}[\progressetaright]\label{def:progressetaright} A link
\linketaM{\Gamma}{X}{T} is removed from \linkStore when either 1)
$\testmaybeeta~T$ does not hold (anymore) or 2) by $\eta$-contracting $T$ to
$T'$, $T'$ is a term not starting with the \elpiIn{lam} constructor. In the
first case, $X$ is unified with $T$ and in the second one, $X$ is unified with
$T'$ (under the context $\Gamma$).
\end{definition}

There is a third case in which a link is removed from \linkStore, namely
when the \lhs is assigned to a variable that is the \lhs of another
\linketa.
